Reasoning About a Machine with Local Capabilities

### 2019-03-06 toplas/paper.tex
[TOPLAS] Fix compilation issue

This last assertion, at line 8 of Figure~\ref{fig:awkward}, should never fail.
From the code, this seems natural, since \texttt{adv} does not have access to $x$.
Therefore, after the second invocation at line 7, $x$ should still be in the state it was before that invocation.
However, consider that \texttt{adv} may have access to $\textit{cl}_x$ and within that second invocation of \texttt{adv}, it may invoke $\textit{cl}_x}$ again.
Then $\textit{cl}_x$ would set $x$ to $0$ again (on line 5) and reinvoke another callback.
If that second callback were somehow able to skip its own caller and return directly to the caller of \texttt{adv}, it would end up at line 8 of Figure~\ref{fig:awkward} with $x$ set to $1$, causing the assertion to fail.
Without going into details, such an attack is perfectly possible if \texttt{adv} has access to a call/cc primitive (or equivalent).
In other words, if we are able to prove that the assertion will never fail, this attack, and other similar attacks, on well-bracketed control flow are adequately prevented.

>>>>

This last assertion, at line 8 of Figure~\ref{fig:awkward}, should never fail.
From the code, this seems natural, since \texttt{adv} does not have access to $x$.
Therefore, after the second invocation at line 7, $x$ should still be in the state it was before that invocation.
However, consider that \texttt{adv} may have access to $\textit{cl}_x$ and within that second invocation of \texttt{adv}, it may invoke $\textit{cl}_x$ again.
Then $\textit{cl}_x$ would set $x$ to $0$ again (on line 5) and reinvoke another callback.
If that second callback were somehow able to skip its own caller and return directly to the caller of \texttt{adv}, it would end up at line 8 of Figure~\ref{fig:awkward} with $x$ set to $1$, causing the assertion to fail.
Without going into details, such an attack is perfectly possible if \texttt{adv} has access to a call/cc primitive (or equivalent).
In other words, if we are able to prove that the assertion will never fail, this attack, and other similar attacks, on well-bracketed control flow are adequately prevented.
